Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-03 ForegroundSimulations/ms.tex
Make minor changes to EoR sensitivity section
From 3e3495b (restructure):
==========================

In ms.tex,

(*) Make minor changes to EoR sensitivity section

\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}

We investigate the effect of chromaticity of power pattern in a {\it foreground avoidance} strategy that avoids the aforementioned deconvolution of delay spectrum. Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}. In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} window function extending 10~MHz on each side centered on 150~MHz with effective bandwidth of 10~MHz. The 8 panels correspond to those shown in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}. As a result of narrowed subband, the resolution in delay space (and $k_\parallel$) has coarsened. The cyan and gray lines denote power spectra of EoR models 1 and 2 respectively.

>>>>

In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} spectral weighting function defined in equation~\ref{eqn:bhw2} with $B_\textrm{eff}=10$~MHz. The 8 panels correspond to those shown in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}. As a result of narrowed subband, the resolution in delay space (and $k_\parallel$) has coarsened. The cyan and gray lines denote power spectra of EoR models 1 and 2 respectively.
